---
title: "2016 Bicycle Crashes in New York by Police Precinct"
author: "Philip Tabak"
date: "November 20, 2017"
output: html_document
---
This map incorporates the [2016 New York City Department of Tranport Bicycle Crash Data](http://www.nyc.gov/html/dot/html/bicyclists/bikestats.shtml#crashdata) and the [NYC OpenData Map of Police Precincts](https://data.cityofnewyork.us/Public-Safety/Police-Precincts/78dh-3ptz).

Each Precinct is drawn on the map, the number of bicycle crashes, injuries to cyclists, fatalities to cyclists, injuries to motor vehiclists and fatalities to motor vehiclists are displayed in a pop when the cursor enters a precinct. Precincts with the highest number of crashes are colored the darkest, and the fewest the lightest.

The bicycle crash data required minimal cleaning: conversion from PowerPoint, naming of columns, removal of subtotals. Cleaned up CSV file is available [here](bicycle_accidents.csv)

Precinct data can be downloaded as a GeoJSON file. The geojsonio library makes the process of drawing this data onto a leaflet map very straightforward.


```{r setup, include=TRUE, echo = TRUE, warning=FALSE, message = FALSE}

library(leaflet)
library(geojsonio)
library(htmltools)
library(rgdal)

#Load data files
precincts <-geojson_read("./Police Precincts.geojson", what = "sp" )
accidents <- read.csv("./bicycle_accidents.csv")
accidents$Precinct <- as.factor(accidents$Precinct ) 

#this will be used to map continuous data to polygon shades on the map. See: https://rstudio.github.io/leaflet/colors.html 
makePallete <- colorNumeric(palette = "Reds", domain = accidents$Crashes)

#This function builds the label HTML.
makeLabels <- function(p, c, i.b, f.b, i.m, f.m){
  r <-  HTML(sprintf("Precinct: %s
                     <br />Crashes: %s
                     <br />Bicyclist Injuries: %s
                     <br />Bicyclist Fatalities: %s
                     <br />Motor Vehicle Occupant Injuries: %s
                     <br />Motor Vehicle Occupant Falities: %s", 
                     htmlEscape(p), 
                     htmlEscape(c), 
                     htmlEscape(i.b), 
                     htmlEscape(f.b), 
                     htmlEscape(i.m), 
                     htmlEscape(f.m)
                     )
             )
  return(r)
}

```



```{r echo = TRUE, fig.height=6, fig.width=9}

leaflet(precincts) %>% 
  addTiles() %>%
  addPolygons( label = mapply(makeLabels, 
                              accidents$Precinct, 
                              accidents$Crashes, 
                              accidents$Bicyclist.Injuries, 
                              accidents$Bicyclist.Fatalities, 
                              accidents$Motor.Vehicle.Occupant.Injuries, 
                              accidents$Motor.Vehicle.Occupant.Fatalities,
                              SIMPLIFY = FALSE),
  color = ~makePallete(accidents$Crashes), fillOpacity = 0.5) 

  
```

